---
title: "What Confucius practiced is good for your mind: Examining the effect of a contemplative practice in Confucian tradition on executive functions"
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A pretest-posttest controlled study comparing BMAA, Chan meditation, and a waitlist control group. Both active interventions included 12 hours of practice over four weeks.

## Key Findings

The clearest finding was that short-term BMAA training improved working-memory capacity. Working memory means the ability to hold information in mind while also using or updating it, such as remembering numbers while doing another task. OSPAN is a working-memory task; higher scores indicate better capacity.

In the figure, the horizontal axis shows pretest and posttest, and each line represents one group. The BMAA group showed a clearer increase than the Chan meditation and waitlist control groups.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = "Working-memory capacity (OSPAN)",
  group = rep(c("BMAA", "Chan meditation", "Waitlist control"), each = 2),
  time = rep(c("Pretest", "Posttest"), 3),
  value = c(3.75, 4.58, 3.52, 3.92, 3.65, 3.98)
)
bmaa_facet_line_plot(dat, "Short-term BMAA and working memory", ylab = "Mean score")
```

## Reference

Teng, S.-C., & Lien, Y.-W. (2016). What Confucius practiced is good for your mind: Examining the effect of a contemplative practice in Confucian tradition on executive functions. *Consciousness and Cognition, 42*, 204-215. https://doi.org/10.1016/j.concog.2016.03.016
