---
title: "BMAA and integrated activity training for improving children’s executive function and emotion regulation"
author: "Chang, Y.-J."
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A pretest-posttest between-group study comparing BMAA-C with an integrated activity program for children.

## Key Findings

The two active programs appeared to help in different ways. BMAA-C showed clearer improvement in working-memory span, while the integrated activity group showed stronger changes in emotion-regulation ratings. Working memory helps children keep and use information during learning; emotion regulation refers to how children manage emotional reactions.

The figure places similar outcomes in separate panels. BMAA-C showed the clearest increase in working memory, whereas the integrated activity group showed stronger changes in emotion-regulation scores.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = rep(c("Working-memory span", "Positive emotion regulation", "Negative emotion regulation"), each = 4),
  group = rep(c("BMAA-C", "BMAA-C", "Integrated activity", "Integrated activity"), 3),
  time = rep(c("Pretest", "Posttest", "Pretest", "Posttest"), 3),
  value = c(37.44, 42.00, 39.08, 40.08, 29.24, 29.84, 30.58, 32.83, 7.88, 8.04, 8.08, 7.17)
)
bmaa_facet_line_plot(dat, "Outcome profile of BMAA-C and integrated activity", ylab = "Mean score")
```

## Reference

張憶如. (2018). *身心中軸覺察與綜合活動訓練增進兒童之執行功能及情緒調節* [碩士論文，中原大學].
