---
title: "Feel your body: Effects of a short-term in-class dynamic contemplative course on children’s interoception, executive control, emotion regulation, and motor coordination"
author: "Lee, M.-N."
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A school-based pretest-posttest control-group study comparing BMAA-C with a waitlist control group over an 11-week course.

## Key Findings

BMAA-C encouraged children to use more self-directed emotion-regulation strategies in negative emotional situations. Seeking help means turning outward to others; reappraisal means looking at the situation from a different angle; breathing relaxation means using the body to calm emotional arousal.

Higher values in the figure mean the child used that strategy more often. After BMAA-C, breathing relaxation and reappraisal increased, while seeking help decreased, suggesting a shift toward more autonomous regulation.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = rep(c("Seeking help", "Reappraisal", "Breathing relaxation"), each = 4),
  group = rep(c("BMAA-C", "BMAA-C", "Control", "Control"), 3),
  time = rep(c("Pretest", "Posttest", "Pretest", "Posttest"), 3),
  value = c(0.85, 0.53, 0.74, 1.13, 0.74, 1.32, 1.26, 1.35, 0.50, 1.41, 0.84, 1.03)
)
bmaa_facet_line_plot(dat, "BMAA-C and self-directed emotion regulation", ylab = "Strategy-use count")
```

## Reference

李茂寧. (2019). *感覺你的身體：短期入班動態靜觀課程對學童內感覺、執行控制功能、情緒調節及運動協調之介入成效* [碩士論文，國立臺灣大學].
