---
title: "Effects of a short-term dynamic body-mind awareness course on elementary school teachers’ interoceptive awareness, resilience, and perceived stress"
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A single-group pretest-posttest study with in-service elementary school teachers. The course included six weeks and 18 hours of BMAA practice.

## Key Findings

After BMAA, teachers reported lower perceived stress, higher resilience, and lower negative affect. Perceived stress reflects how stressful life feels; resilience refers to the ability to recover from stress; PANAS negative affect captures unpleasant emotional states such as worry, tension, or irritability.

The directions differ by variable: lower stress and negative affect are better, while higher resilience is better. Overall, the pattern suggests reduced stress burden and improved recovery capacity.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = rep(c("Perceived stress (PSS)", "Resilience (BRS)", "PANAS negative affect"), each = 2),
  group = rep("Teacher BMAA", 6),
  time = rep(c("Pretest", "Posttest"), 3),
  value = c(16.00, 10.28, 3.33, 3.83, 2.26, 1.65)
)
bmaa_facet_line_plot(dat, "BMAA reduced stress and supported resilience in teachers", ylab = "Mean score")
```

## Reference

翁宛婷. (2020). *探討短期動態身心覺察課程對國小教師內感覺覺察、心理韌性與壓力知覺的介入成效* [碩士論文，國立臺灣師範大學].
