---
title: "Effects of BMAA combined with lucid-dream therapy on lucid dreaming, nightmares, and sleep quality among people with nightmare distress"
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A pretest-posttest control-group study comparing a BMAA-MILD intervention with a waitlist control group. The intervention combined BMAA practice, lucid-dream induction training, reality testing, and dream journaling.

## Key Findings

BMAA-MILD combined body awareness with lucid-dream induction skills. Lucidity reflects how aware a person is that they are dreaming while in the dream; NDQ reflects nightmare distress; PSQI reflects sleep quality, with lower scores indicating better sleep.

The BMAA-MILD group showed increased lucidity and reduced nightmare distress and sleep-quality problems, while the control group changed less.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = rep(c("Lucidity", "Nightmare distress (NDQ)", "Sleep quality (PSQI)"), each = 6),
  group = rep(c("BMAA-MILD", "BMAA-MILD", "BMAA-MILD", "Control", "Control", "Control"), 3),
  time = rep(c("Pretest", "Midtest", "Posttest", "Pretest", "Midtest", "Posttest"), 3),
  value = c(54.90, 61.71, 72.43, 66.04, 65.91, 65.48, 23.52, 22.81, 16.76, 25.43, 24.70, 23.39, 8.57, 7.67, 6.10, 9.35, 9.78, 9.74)
)
bmaa_facet_line_plot(dat, "BMAA-MILD and lucid dreaming, nightmares, and sleep", ylab = "Mean score")
```

## Reference

邱敬惠. (2024). *身心中軸覺察訓練結合清醒夢療法對惡夢困擾者的清醒夢、惡夢與睡眠品質的影響* [碩士論文，中原大學].
