---
title: "Improving interoceptive ability to reduce internet addiction tendency: Effects and mechanisms of BMAA training"
author: "Mou, S.-C."
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A randomized pretest-posttest control-group study with participants who scored high on internet addiction tendency. The BMAA group received a six-week, 12-hour BMAA course with daily home practice.

## Key Findings

After six weeks of BMAA, internet addiction tendency decreased, especially in core symptoms. CIAS total score reflects overall internet addiction risk; core symptoms include difficulty controlling use, withdrawal-like feelings, and tolerance-like increases in use.

The BMAA group showed a larger decrease from pretest to posttest than the control group. This suggests that improving bodily awareness may help people notice urges and regulate internet-use behavior.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = rep(c("CIAS total", "Core internet-addiction symptoms"), each = 4),
  group = rep(c("BMAA", "BMAA", "Control", "Control"), 2),
  time = rep(c("Pretest", "Posttest", "Pretest", "Posttest"), 2),
  value = c(74.84, 62.37, 75.35, 71.35, 41.79, 35.26, 42.90, 40.65)
)
bmaa_facet_line_plot(dat, "BMAA reduced internet addiction tendency", ylab = "Mean score")
```

## Reference

牟書琪. (2024). *內感覺能力提升對於降低網路成癮傾向的影響：以身心中軸覺察訓練為介入的效果與機制探討* [碩士論文，中原大學].
