---
title: "From the body to the mind: Interoception and sense of agency as mechanisms of depression reduction in BMAA"
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A pretest-posttest active-control study with university students. The BMAA group received a ten-week, 30-hour program, while the active-control group joined body-mind related reading discussions.

## Key Findings

This study connects BMAA to a possible mechanism: improved body awareness may reduce feelings of helplessness or loss of control, which may then reduce depression. BDI measures depressive symptoms; lower scores are better. SoNA measures negative sense of agency, or the feeling that one cannot influence one’s own state. MAIA Self-regulation reflects the ability to use body awareness to calm or regulate oneself.

The BMAA group showed lower depression and negative agency, along with higher interoceptive self-regulation. The active-control group changed less.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = rep(c("Depression (BDI)", "Negative agency (SoNA)", "Interoceptive self-regulation"), each = 4),
  group = rep(c("BMAA", "BMAA", "Active control", "Active control"), 3),
  time = rep(c("Pretest", "Posttest", "Pretest", "Posttest"), 3),
  value = c(15.62, 7.89, 11.00, 11.95, 2.96, 2.40, 2.55, 2.66, 2.65, 3.66, 2.88, 3.02)
)
bmaa_facet_line_plot(dat, "BMAA, body awareness, agency, and depression", ylab = "Mean score")
```

## Reference

Lien, Y.-W., Teng, S.-C., & Wei, L.-Y. (2026). From the body to the mind: Interoception and sense of agency as mechanisms of depression reduction in the Body-Mind Axial Awareness (BMAA). *Frontiers in Psychology, 17*, Article 1755698. https://doi.org/10.3389/fpsyg.2026.1755698
