---
title: "From body to mind: How body-mind axial awareness training enhances body awareness, mindfulness, positive embodiment and mental health in healthcare students"
lang: en
language: ../../assets/language-en.yml
toc-title: "On this page"
---

```{r}
#| include: false
source("../../R/bmaa_plot_theme.R")
```

## Method

A non-randomized pretest-posttest control-group study with healthcare students. The BMAA group received an eight-week BMAA program with weekly practice, home practice, and written reflection.

## Key Findings

Healthcare students showed positive changes in body awareness, mental health, and emotional expression after BMAA. BAAI measures body awareness; AMHS reflects mental health, with higher scores indicating better functioning; TAS-20 measures alexithymia, so lower scores indicate less difficulty identifying and expressing emotions.

The BMAA group increased in body awareness and mental health and decreased in alexithymia, while the control group changed less or moved in the opposite direction.

```{r}
#| fig-height: 4.8
dat <- data.frame(
  outcome = rep(c("Body awareness (BAAI)", "Mental health (AMHS)", "Alexithymia (TAS-20)"), each = 4),
  group = rep(c("BMAA", "BMAA", "Control", "Control"), 3),
  time = rep(c("Pretest", "Posttest", "Pretest", "Posttest"), 3),
  value = c(92.74, 99.87, 95.74, 94.85, 94.08, 101.00, 101.70, 99.44, 47.32, 43.13, 51.44, 50.81)
)
bmaa_facet_line_plot(dat, "BMAA improved body and mental-health indicators in healthcare students", ylab = "Mean score")
```

## Reference

Tien, Y.-M., Lin, C.-Y., Lien, Y.-W., & Hsu, L.-C. (2026). From body to mind: How body-mind axial awareness training enhances body awareness, mindfulness, positive embodiment and mental health in healthcare students. *Health Psychology and Behavioral Medicine, 14*(1), Article 2656029. https://doi.org/10.1080/21642850.2026.2656029
